---
title: "R Notebook"
output: html_notebook
---

```{r}
compare_m_gibbs <- function(y, ind, maxiter = 5000)
{
  
### weakly informative priors
a0 <- 1/2 ; b0 <- 50 ## tau_w hyperparameters
eta0 <-1/2 ; t0 <- 50 ## tau_b hyperparameters
mu0<-50 ; gamma0 <- 1/25
###
a0 <- 1.9 ; b0 <- 1 ## tau_w hyperparameters
eta0 <-1/2 ; t0 <- 5 ## tau_b hyperparameters
mu0<-3.5 ; gamma0 <- 1.25
###



### starting values
m <- nlevels(ind)
ybar <- theta <- tapply(y, ind, mean)

temp = tapply(y, ind, var)
temp = temp[!is.na(temp)]
tau_w <- 1/mean(temp) ##within group precision
mu <- mean(theta)
tau_b <-var(theta) ##between group precision
n_m <- tapply(y, ind, length)
an <- a0 + sum(n_m)/2
###

### setup MCMC
theta_mat <- matrix(0, nrow=maxiter, ncol=m)
mat_store <- matrix(0, nrow=maxiter, ncol=3)
###
### MCMC algorithm
for(s in 1:maxiter) 
{
  
  # sample new values of the thetas
  for(j in 1:m) 
  {
    taun <- n_m[j] * tau_w + tau_b
    thetan <- (ybar[j] * n_m[j] * tau_w + mu * tau_b) / taun
    theta[j]<-rnorm(1, thetan, 1/sqrt(taun))
  }
  
  #sample new value of tau_w
  ss <- 0
  for(j in 1:m){
    ss <- ss + sum((y[ind == j] - theta[j])^2)
  }
  bn <- b0 + ss/2
  tau_w <- rgamma(1, an, bn)
  
  #sample a new value of mu
  gammam <- m * tau_b + gamma0
  mum <- (mean(theta) * m * tau_b + mu0 * gamma0) / gammam
  mu <- rnorm(1, mum, 1/ sqrt(gammam)) 
  
  # sample a new value of tau_b
  etam <- eta0 + m/2
  tm <- t0 + sum((theta-mu)^2)/2
  tau_b <- rgamma(1, etam, tm)
  
  #store results
  theta_mat[s,] <- theta
  mat_store[s, ] <- c(mu, tau_w, tau_b)
}
colnames(mat_store) <- c("mu", "tau_w", "tau_b")
return(list(params = mat_store, theta = theta_mat))
}
```

```{r}
library(zoo)
library(httr)
library(readr)
library(ggpubr)
library(plotly)
library(mclust)
library(ggplot2)
library(reshape)
library(stringr)
library(MCMCpack)
library(BayesLCA)
library(jsonlite)
library(tidyverse)

#install.packages("ggpubr")
```

```{r}

##Business_Toronto_Restaurant.json
path = "C:/Users/Swastik/Desktop/MastersDegree_CS/Semester_2/AppliedStatisticalModelling/ass_2/data/Business_Toronto_Restaurant.json"
df_toronto <- stream_in(file(path), flatten = TRUE)

#path = "C:/Users/Swastik/Desktop/MastersDegree_CS/Semester_2/AppliedStatisticalModelling/ass_2/data/_all/business.json"
#df_original <- stream_in(file(path))
 
#df_toronto <- flatten(df_toronto)
#df_toronto$neighborhood

```


```{r}

df_indian <- df_toronto[str_detect(df_toronto$categories, "India|india|INDIA"),] 

nrow(df_indian)
df_indian_open <- df_indian[df_indian$is_open == 1,]
df_indian_open_min_4review <- df_indian_open[df_indian_open$review_count > 3,]

df_ek_indian <- df_indian[df_indian$neighborhood == "Etobicoke",]
df_sb_indian <- df_indian[df_indian$neighborhood == "Scarborough",]
df_ek_indian_open_min_4review <- df_indian_open_min_4review[df_indian_open_min_4review$neighborhood == "Etobicoke",]
df_sb_indian_open_min_4review <- df_indian_open_min_4review[df_indian_open_min_4review$neighborhood == "Scarborough",]


df_indian_open_min_4review$neighborhood <- factor(df_indian_open_min_4review$neighborhood)
nlevels(df_indian_open_min_4review$neighborhood)
df_indian_open_min_4review$neighborhood <- as.numeric(df_indian_open_min_4review$neighborhood)

nrow(df_indian_open)
nrow(df_indian_open_min_4review)
nrow(df_ek_indian)
nrow(df_sb_indian)
nrow(df_ek_indian_open_min_4review)
nrow(df_sb_indian_open_min_4review)

mean(df_indian_open_min_4review$stars)
mean(df_ek_indian_open_min_4review$stars)
mean(df_sb_indian_open_min_4review$stars)
mean(df_ek_indian$stars)
mean(df_sb_indian$stars)
```

```{r}
df_ek_indian$business_id
x <- df_indian_open_min_4review[df_indian_open_min_4review$business_id == "ZPhQyUO9MY5xNEcTqZOrTQ",]
x
```

```{r}
ggplot(df_ek_indian) + geom_boxplot(aes(x = reorder(neighborhood, stars, median), stars, fill = reorder(neighborhood, stars, median)), show.legend=TRUE)
```
```{r}
ggplot(df_sb_indian) + geom_boxplot(aes(x = reorder(neighborhood, stars, median), stars, fill = reorder(neighborhood, stars, median)), show.legend=TRUE)
```

```{r}
ggplot(df_indian_open_min_4review[df_indian_open_min_4review$neighborhood == 14 | df_indian_open_min_4review$neighborhood == 33,]) + geom_boxplot(aes(x = reorder(neighborhood, stars, median), stars, fill = reorder(neighborhood, stars, median)), show.legend=FALSE)
```


```{r}
ggplot(df_indian_open_min_4review[df_indian_open_min_4review$neighborhood == 33|df_indian_open_min_4review$neighborhood == 14,], aes(x = neighborhood, y = stars)) + 
  geom_violin(aes(x = reorder(neighborhood, stars, median), stars, fill = reorder(neighborhood, stars, median)), show.legend = FALSE)
```
```

```{r}
ggplot(df_indian_open_min_4review) + geom_boxplot(aes(x = reorder(neighborhood, stars, median), stars, fill = reorder(neighborhood, stars, median)), show.legend=FALSE)
```

```{r}
#stars Vs count 
ggplot(df_sb_indian_open_min_4review, aes(stars)) + stat_bin()

```

```{r}
#stars Vs count 
ggplot(df_ek_indian_open_min_4review, aes(stars)) + stat_bin()

```


```{r}

# neighbourhood vs count
ggplot(df_indian_open_min_4review, aes(x = reorder(neighborhood, neighborhood, length))) + stat_count()
```
 

```{r}
df2 <- df_indian_open_min_4review[df_indian_open_min_4review$business_id %in% c("OGSWuGLLW_8TBmQ_wWhdEQ","YLeAUkFFJri_21uTkyrVFg"),]
df2

```

```{r}
df2 <- df_indian_open_min_4review[df_indian_open_min_4review$neighborhood %in% c(14,33),]

#Etobicoke : 14
#Scarborough : 33


fit_1 <- compare_m_gibbs(df2$stars, factor(df2$neighborhood))

#fit_1 <- compare_m_gibbs(df_indian_open_min_4review$stars, factor(df_indian_open_min_4review$neighborhood))

apply(fit_1$params, 2, mean)
apply(fit_1$params, 2, sd)
mean(1/sqrt(fit_1$params[, 3]))
sd(1/sqrt(fit_1$params[, 3]))

theta_hat <- apply(fit_1$theta, 2, mean)
ggplot(data.frame(size = tapply(df_indian_open_min_4review$stars, df_indian_open_min_4review$neighborhood, length), theta_hat = theta_hat), aes(size, theta_hat)) + geom_point()
```


```{r}
#Normality tests
#p-value > 0.05 implies that we can assume the normality.
shapiro.test(rnorm(100, mean = 5, sd = 3))
shapiro.test(runif(100, min = 2, max = 4))

#Bell Shape == Normal distribution
ggdensity(rnorm(100, mean = 5, sd = 3), 
          main = "Density plot of ratings",
          xlab = "Ratings")

#If points are close to the 45 degree line -> normal distribution
ggqqplot(rnorm(100, mean = 5, sd = 3)) 

shapiro.test(df_ek_indian_open_min_4review$stars)
ggdensity(df_indian_open_min_4review$stars, 
          main = "Density plot of ratings",
          xlab = "Ratings")

ggqqplot(df_ek_indian_open_min_4review$stars)

```

